\section{Lessons learned}\label{sec:lessons-learned}
% Erkenntnisse zu Rahmenbedingungen, Zusammenarbeit (im Team, Fachbetreuer, PM-Coach, Kunde, Betreiber, etc.)
% Insights into framework conditions, cooperation (in the team, specialist advisor, PM coach, customer, operator, etc.)

\subsection{Insights into framework conditions}\label{subsec:insights-into-framework-conditions}
For the team members which already had quite some experience with Scrum,
there was still the learning curve of setting up everything from scratch.
The other member had quite some experience with alternative forms of agile software development and could learn a lot about the Scrum specific methods.
In our point of view, the most important Scrum ceremonies were the sprint review and planning
which we always held subsequently.
The sprint review resulted in some interesting demos, kept the whole team in sync, showed the current progress, and
already indicated what the next steps could be.
On the other hand there is no sprint without the sprint planning and after it, every team member knows what he has to do next.
In the context of project 1 the key takeaway for the project team is, that Scrum also works when nobody works full-time
on the project and all the work is done remotely.

\subsection{Cooperation}\label{subsec:cooperation}
\paragraph{Team:}
The key challenge for the project team in terms of cooperation was the limbo between working, other modules, and project 1.
This resulted in the reality that we only worked together in the modules official time block.
In the beginning a project member had issues being on time for meetings, but luckily he could resolve this issue.
Besides the minor challenges and issues, the team work was amazing, and we enjoyed working together.

\paragraph{Specialist advisor / Stakeholder:}
We consider the cooperation with Dr. Kramer as good, as he communicated his expectations clearly from the start.
If we had issues or questions we received an answer within reasonable time or could schedule a meeting with him in the
modules official time block.

\paragraph{Project Management Coach:}
The cooperation needed with the project management coach was minimal as all requirements were clearly documented in moodle.
When something was unclear we received an answer within reasonable time.
