\section{Project Setup Review}\label{sec:project-setup-review}
% Erfassung der Ausgangssituation, Themen-Analyse, Stakeholder(-Management), Organisation, Installationen
% Identifying the initial situation, topic analysis, stakeholder (management), organisation, installations

\subsection{Identifying the initial situation}\label{subsec:identifying-the-initial-situation}
For identifying the initial situation we analysed~\ref{subsec:project-description} Project Description and used multiple online resources
such as the websites of \href{https://laermliga.ch/}{Lärmliga Schweiz} and \href{https://www.bafu.admin.ch/bafu/en/home/topics/noise/in-brief.html}{Federal Office for the Environment FOEN}.
Based on those information we were able to derive some of the requirements and specifications for our application,
which now provides a convenient way for affected people to document noise pollution.

\subsection{Topic analysis}\label{subsec:topic-analysis}
To solve the issue at hand, one needs knowledge about how audio recoding and measurement works.
We invested the time needed to analyse the topic and gather the know-how needed to process and analyse audio files.
A short summary of the problematic can be found under~\ref{subsec:problems-with-audio-files} Problems with Audio Files.
This analysis provided the technical basis for achieving the product goal.

\subsection{Stakeholder / Stakeholder Management}\label{subsec:stakeholder-management}
Initially we identified a list of possible stakeholders:

\begin{itemize}
    \item Tutor: Dr. Simon Kramer
    \item People affected by noise pollution
    \item Noise producers (Construction Sites, Night Clubs, Highways)
    \item Lärmliga Schweiz
    \item Federal Office for the Environment FOEN
\end{itemize}

For the context of this module we decided to only consider our tutor as the sole stakeholder,
because otherwise the stakeholder management would cost much more time without much benefit.
This way the stakeholder management turned out to be straight forward, as Dr. Kramer provided his expectations and the
scope of the project beforehand, only impediments and key decisions had to be discussed together.

\subsection{Organisation}\label{subsec:organisation}
TODO: Ask what is wanted here

\subsection{Installations}\label{subsec:installations}
TODO: Ask what is wanted here
